### 2018-12-06 chapters/4-discussion.tex
readability

Most studies on texture analysis of PCa include only a small number of texture
descriptors and configurations \citep{Kwak2015, Viswanath2012, Ginsburg2014}. In
this study, we utilized a large number of both, from multiparametric source.
This allows evaluating a huge number of feature combinations.

Texture analysis of multiparametric MRI has previously seen limited use in PCa
characterization. \citet{Fehr2015} evaluated PCa characterization with the
whole-lesion 1st order statistics and GLCM texture features from a similar-size
dataset of ADC and T₂w. They used oversampling to ward off effect of class
imbalance. Similarly to our study, they integrated dynamic feature selection as
part of the training (using the recursive feature selection support vector
machine, RFE-SVM). In our study, we included a much more diverse and numerous
set of features, as one of our goals was to evaluate various texture extraction
methods. Moreover, we have for the first time demonstrated that using texture
features from K (kurtosis function) provided improvements to ADCₘ
(monoexponential function). This is important since first order statistics of
parameters derived from kurtosis function do not lead to improved performance of
ADCm (monoexponential function). The effect of noise remains to be explored in
future studies.

\citet{Tiwari2013} classified PCa using GLCM and simple gradient features from
T₂w and MR spectroscopy (MRS). A multi-kernel classifier with graph embedding
was used to reduce dimensionality. \citet{Tiwari2013} had fewer patients
compared to the current study. Moreover, the classification was done on
equally-sized, rectangular metavoxels.

@@

Contrarily to previous approaches to performing non-rigid deformation and
co-registration of datasets with subsequent resampling to common space and
resolution \citep{Viswanath2012, Ginsburg2014}, in the current study the
prostate and tumor masks were done for each MR imaging method (T₂w, DWI, T₂)
individually, allowing us to perform texture analyses at their original native
resolutions. Estimating the effect of co-registration and resampling on texture
extraction is not trivial, and the process could cause loss of information.
However, the accuracy of the delineations in this study could be potentially
improved by an added step of co-registering MRI to histology images
\citep{Bourne2017}. We highlight the limitation of performing re-slicing and
non-rigid deformation of MR data sets to common space and then co-registering
with whole mount prostatectomy sections. As correctly noted by
\citet{Bourne2017}, co-registration of whole mount prostatectomy sections to MRI
data sets is important. However, the effect of re-slicing and non-rigid
deformation of MR data sets to common space remains to be explored.

The gray-level co-occurrence matrix may well be the most widely used tool for
texture analysis of prostate MRI data sets. The Sobel operator, Gabor filters,
Haar transform, and local binary patterns have already extensively been applied
for texture analysis of prostate MRI, as have a few others~\citep{Lemaitre2015}
not included in this study.

@@

We have evaluated an extensive number of MRI texture features in multivariate
setting for their ability to predict the Gleason score of prostate cancer.
Moreover, we have presented a machine learning system that, from a very large
number of candidate features, searches for a relevant subset for the task and
alternatively weights the features accordingly. The single feature with highest
prediction performance estimate (AUC = 0.84) was a gray-level co-occurrence
matrix homogeneity of T₂w. The Gabor transform features performed well with the
ADC and K parameters. The lowest percentile statistics were useful with ADC and
T₂w. The features based on Hu and Zernike moments performed well for K and T₂.
Our results imply that a specific set of features and feature extraction methods
is needed to obtain maximal information from DWI, T₂w, and T₂. The highest
overall performance estimate (AUC = 0.88) was obtained for the model utilizing a
small subset of texture features from the ADCₘ, K, and T₂w parameters. These
features included texture descriptors based on gray-level co-occurrence matrix,
Gabor transform, and the Zernike and Hu moments.

>>>>

Most studies on texture analysis of PCa include only a small number of texture
descriptors and configurations \citep{Kwak2015, Viswanath2012, Ginsburg2014}. In
this study, we utilized a large number of both, from multiparametric source.
This allows evaluating a huge number of feature combinations, as the
regularization prevents overfitting caused by high dimensionality.

Texture analysis of multiparametric MRI has previously seen limited use in PCa
characterization. \citet{Fehr2015} evaluated PCa characterization with the
whole-lesion first order statistics and GLCM texture features from a
similar-size dataset of ADC and T₂w. They used oversampling to ward off effect
of class imbalance. Similarly to our study, they integrated dynamic feature
selection as part of the training (using the recursive feature selection support
vector machine, RFE-SVM). In our study, we included a much more diverse and
numerous set of features, as one of our goals was to evaluate various texture
extraction methods. Moreover, we have for the first time demonstrated that using
texture features from K (kurtosis function) provided improvements to ADCₘ
(monoexponential function). This is important since first order statistics of
parameters derived from kurtosis function do not lead to improved performance of
ADCm (monoexponential function). The effect of noise remains to be explored in
future studies.

\citet{Tiwari2013} classified PCa using GLCM and simple gradient features from
T₂w and MR spectroscopy (MRS). A multi-kernel classifier with graph embedding
was used to reduce dimensionality. Compared to the current study, they had fewer
patients, and the classification was done on equally-sized, rectangular
metavoxels.

@@

Contrarily to previous approaches to performing non-rigid deformation and
co-registration of datasets with subsequent resampling to common space and
resolution \citep{Viswanath2012, Ginsburg2014}, in the current study the
prostate and tumor masks were done for each MR imaging method (T₂w, DWI, T₂)
individually, allowing us to perform texture analyses at their original native
resolutions. Estimating the effect of co-registration and resampling on texture
extraction is not trivial, and the process could cause loss of information.
However, the accuracy of the delineations in this study could be potentially
improved by an added step of co-registering MRI to histology images
\citep{Bourne2017}.

We highlight the limitation of performing re-slicing and
non-rigid deformation of MR data sets to common space and then co-registering
with whole mount prostatectomy sections. As correctly noted by
\citet{Bourne2017}, co-registration of whole mount prostatectomy sections to MRI
data sets is important. However, the effect of re-slicing and non-rigid
deformation of MR data sets to common space remains to be explored.

The gray-level co-occurrence matrix may well be the most widely used tool for
texture analysis of prostate MRI data sets. The Sobel operator, Gabor filters,
Haar transform, and local binary patterns have already been extensively applied
for texture analysis of prostate MRI, as have a few others~\citep{Lemaitre2015}
not included in this study.

@@

We have evaluated an extensive number of MRI texture features in multivariate
setting for their ability to predict the Gleason score of prostate cancer.
Moreover, we have presented a machine learning system that, from a very large
number of candidate features, searches for a relevant subset for the task and
alternatively weights the features accordingly.

The single feature with highest
prediction performance estimate (AUC = 0.84) was a gray-level co-occurrence
matrix homogeneity of T₂w. The Gabor transform features performed well with the
ADC and K parameters. The lowest percentile statistics were useful with ADC and
T₂w. The features based on Hu and Zernike moments performed well for K and T₂.
Our results imply that a specific set of features and feature extraction methods
is needed to obtain maximal information from DWI, T₂w, and T₂.

The highest
overall performance estimate (AUC = 0.88) was obtained for the model utilizing a
small subset of texture features from the ADCₘ, K, and T₂w parameters. These
features included texture descriptors based on gray-level co-occurrence matrix,
Gabor transform, and the Zernike and Hu moments.
